Improving \textsl{Gaia} parallaxes with a data-driven model \\ of the color--magnitude diagram

### 2017-05-03 paperDistance/paper.tex
paper tweaks

\subsection{Proper Dust Corrections}
Within our probabilistic framework, we improperly handle dust. We are taking a point estimate of the probabilistic dust model at a quantile distance of our posterior, correcting our photometry using this point estimate and rederiving the prior in \xd. A full, proper account would sample the dust model at distances sampled from the posterior and propagate those samples back into \xd during the iterative proccess. The issues is that this dust sample distribution would not be a Gaussian distribution which \xd\ requires. We could calculate this more complex dust distribution and estimate it as a Gaussian distribution to feed to \xd, however, this is beyond the scope of this paper.

\subsection{Stationarity Assumption}
Both the low and high signal to noise objects are being drawn from the same distribution, independent of noise. This isn't precisely true because most Gaia objects have similar noise but their signal depends on their distance. Nearby stars have higher signal (parallax) because they are closer and the nearby stars are mostly main sequence stars (IMF, timing, malmquist). We can see bright giants to much larger distances and therefore lower signal or parallax and lower signal to noise. So the red giant branch is a population of relatively lower signal to noise objects than the main sequence. But I think this is ok, that the low and high signal to noise objects have to be drawn from the same distribution within some feature or patch of the space. This is all assuming the Gaia noise model is correct. If the uncertainties are over estimated then we could be over deconvolving (generating a tighter distribution than the truth) And in some extreme over estimate of uncertainties the lower signal to noise giants could be pulled to the main sequence. But with the quoted uncertainties this seems unlikely. As you move up the giant branch and probe farther giants the signal to noise will continue to diminish but I think this is okay since the color uncertainties are not large. Possibly a metallicity trend with distance, placing more nearby (higher S/N) objects at slightly different positions on the CMD pulling lower S/N objects to that distribution for our prior. But if something has small error bars is good data is good data both for inference and generating the prior

>>>>

\subsection{Proper Dust Corrections}
Within our probabilistic framework, we improperly handle dust. We are taking a point estimate of the probabilistic dust model at a quantile distance of our posterior, correcting our photometry using this point estimate and rederiving the prior. A full, proper account would sample the dust model at distances sampled from the posterior and propagate those samples back into the prior during the iterative proccess. The issue, the reason we don't do a full probabilistic treatment, is that this proper dust distribution would not be a Gaussian distribution which \xd\ requires. We could calculate this more complex dust distribution and estimate it as a Gaussian distribution to feed to \xd, however, this is beyond the scope of this paper.

\subsection{Stationarity Assumption}
Stationarity assumes both the low and high signal to noise objects are being drawn from the same distribution, independent of noise. This isn't precisely true because most Gaia objects have similar noise $(\sim 3 mas)$, but their signal (parallax) depends on their distance. Nearby stars have higher signal (parallax) because they are closer and the nearby stars are mostly main sequence stars (IMF, timing, malmquist). However, we can see bright giants to much larger distances and therefore lower signal or parallax, leading to lower signal to noise. So the red giant branch is a population of relatively lower signal to noise objects compared with the main sequence. But I think this is ok, that the low and high signal to noise objects have to be drawn from the same distribution within some feature or patch of the space. This is all assuming the Gaia noise model is correct. If the uncertainties are over estimated then we could be over deconvolving (generating a tighter distribution than the truth) And in some extreme over estimate of uncertainties the lower signal to noise giants could be pulled to the main sequence. But with the quoted uncertainties this seems unlikely. As you move up the giant branch and probe farther giants the signal to noise will continue to diminish but I think this is okay since the color uncertainties are not large. Possibly a metallicity trend with distance, placing more nearby (higher S/N) objects at slightly different positions on the CMD pulling lower S/N objects to that distribution for our prior. But if something has small error bars is good data is good data both for inference and generating the prior
